Direct observation of \swave scattering of fermions crossing a Feshbach resonance

### 2015-03-10 draft1.tex
Finished making all the pictures look nice!

\begin{document}
\newcommand{\swave}[0]{$\it{s}$-wave }
\newcommand{\pwave}[0]{$\it{p}$-wave }
\newcommand{\K}{ $^{40}\rm{K}$}

@@

\caption{Predictions for optical density as a function of probe intensity for an imaging time $t=50\mu s$. Note that the two versions of simulated optical density, $\nu_{corr1}$ and $\nu_{corr2}$ are virtually indistinguishable. }  

@@

\caption{The optical density as a function of probe intensity for three imaging times: $t=40\mu \rm{s}$ (blue),  $t=75\mu \rm{s}$ (green),  $t=100\mu \rm{s}$ (red). The dots represent experimental data and the lines represent the best fit of simulated data. The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/us. }  

@@

\par As seen in figure \ref{fig:SNR}, around 40$\mu s$ for reasonable parameters the uncertainty levels out and there are no longer appreciable benefits by extending the imaging time. The advantage of going to a 40$\mu s$ as opposed to 10$\mu s$ where the uncorrected model is appropriate is about a factor of  1.6 reduction in measurement uncertainty. 

@@

	\subfigure[]{\includegraphics[scale=0.45]{figure9a}}
	\subfigure[]{\includegraphics[scale=0.45]{figure9b}}
\caption{Dependance of detection uncertainty of optical depth on imaging time, after correcting for recoil induced detuning. a. Uncertainty at fixed probe intensity $I_0/I_{sat}=2.6$ for a range of optical depths and b. fixed $OD=1.5$ for a range of probe intensities.}  

@@

\par We then use a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice. Since the initial Fermi gas has a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms are successfully transferred into the 1st excited band of the lattice. We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely. The optimized pulse times are 23$\mu s$ for the first square pulse, 13$\mu s$ off interval, and 12$\mu s$ for the second square pulse. 
\par We release the atoms from the trap and allow 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way. For the data taken coming from below the Feshbach resonance, we then simply ramp down the field and image the atoms. For the data taken coming from above the Feshbach resonance, we then ramp the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramp the field back down and image the atoms. We use an imaging pulse of 40$\mu s$.

@@

	\subfigure[]{\includegraphics[scale=0.8]{figure10a}}
	\subfigure[]{\includegraphics[scale=0.8]{figure10b}}

@@

	\includegraphics[scale=0.57]{figure12}
\caption{Scattered fraction over the total atom number as a function of bias field. Green dots represent data taken coming from below the resonance, and blue dots represent the data taken coming from above the resonance. Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit. The four points in the middle were not used in the fit at all, as they are in the regime where the scattering length is large enough for the atoms to behave hydrodynamically and the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.   }  

@@

We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of ~40$\mu s$ for $^{40}K$ atoms for noise minimization after corrections. We use these results to observe s-wave scattering halos of the Fermi gas around the Feshbach resonance and directly verify the resonance location and width. Our analysis can be used in any absorption imaging applications where signal to noise minimization is critical. Experimental techniques devoloped for our s-wave scattering expeiment can be readily extended to a Raman-coupled single component gas version, in which we hope to detect synthetic p-wave interactions. 

>>>>

\begin{document}
\newcommand{\swave}[0]{$\it{s}$-wave }
\newcommand{\pwave}[0]{$\it{p}$-wave }
\newcommand{\K}{ $^{40}\rm{K}$}
\newcommand{\us}{$\mu \rm{s}$}

@@

\caption{Predictions for optical density as a function of probe intensity for an imaging time $t=50$\us. Note that the two versions of simulated optical density, $\nu_{corr1}$ and $\nu_{corr2}$ are virtually indistinguishable. }  

@@

\caption{The optical density as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red). The dots represent experimental data and the lines represent the best fit of simulated data. The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/\us{}. }  

@@

\par As seen in figure \ref{fig:SNR}, around 40\us{} for reasonable parameters the uncertainty levels out and there are no longer appreciable benefits by extending the imaging time. The advantage of going to a 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate is about a factor of  1.5 increase in signal to noise ratio. 

@@

	\subfigure[]{\includegraphics{figure9a.pdf}}
	\subfigure[]{\includegraphics{figure9b.pdf}}
\caption{Signal to noise ratio [SNR] for three different optical depths after correcting for recoil induced detuning. a. SNR as a function of probe intensity $I_0/I_{sat}=5.0$ and b. SNR as a function of probe intensity for an imaging time of 50\us{}.}  

@@

\par We then use a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice. Since the initial Fermi gas has a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms are successfully transferred into the 1st excited band of the lattice. We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely. The optimized pulse times are 23\us{} for the first square pulse, 13\us{} off interval, and 12\us{} for the second square pulse. 
\par We release the atoms from the trap and allow 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way. For the data taken coming from below the Feshbach resonance, we then simply ramp down the field and image the atoms. For the data taken coming from above the Feshbach resonance, we then ramp the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramp the field back down and image the atoms. We use an imaging pulse of 40\us{}.

@@

	\subfigure[]{\includegraphics{figure10a.pdf}}
	\subfigure[]{\includegraphics{figure10b.pdf}}

@@

	\includegraphics{figure11.pdf}
\caption{Normalized scattered population plotted versus bias field B. Green dots represent data taken coming from below the resonance, and blue dots represent the data taken coming from above the resonance. Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit. The regime where the scattering length is large enough for the atoms to behave hydrodynamically is shaded in grey. Data points in that region were not used in the fit, as there the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid. Values for the resonant field $B_0$ from literature and as found in this work are indicated.    }  

@@

We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of ~40\us{} for $^{40}K$ atoms for noise minimization after corrections. We use these results to observe s-wave scattering halos of the Fermi gas around the Feshbach resonance and directly verify the resonance location and width. Our analysis can be used in any absorption imaging applications where signal to noise minimization is critical. Experimental techniques devoloped for our s-wave scattering expeiment can be readily extended to a Raman-coupled single component gas version, in which we hope to detect synthetic p-wave interactions. 
